Leveraging Sparsity to Speed Up Polynomial Feature Expansions of CSR Matrices Using $K$-Simplex Numbers

### 2018-04-11 paper/Final/iccsda_sparse_poly.tex
abstract tweaks

\begin{abstract}
%\boldmath
An algorithm is provided for performing polynomial feature expansions whose input and output are compressed sparse row (CSR) matrices.
Previously, no such algorithm existed, and performing these expansions on CSR matrices required an intermediate densification step.
%The algorithm operates on and produces a compressed sparse row matrix with no densification.
The algorithm works by using a bijective function involving simplex numbers of column indices in the original matrix to column indices in the expanded matrix.
Not only is space saved by working only in CSR format, but the bijective function allows for only the nonzero elements to be iterated over and multiplied together during the expansion, greatly improving average time complexity.
For a vector of dimension $D$ and density $0 \le d \le 1$, the algorithm has time complexity $\Theta(d^KD^K)$ where $K$ is the polynomial-feature order; this  is an improvement by a factor $d^K$ over the standard method.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

>>>>

\begin{abstract}
%\boldmath
An algorithm is provided for performing polynomial feature expansions that both operates on and produces compressed sparse row (CSR) matrices.
Previously, no such algorithm existed, and performing these expansions on CSR matrices required an intermediate densification step.
%The algorithm operates on and produces a compressed sparse row matrix with no densification.
The algorithm performs a $K$-degree expansion by using a bijective function involving $K$-simplex numbers of column indices in the original matrix to column indices in the expanded matrix.
Not only is space saved by working only in CSR format, but the bijective function allows for only the nonzero elements to be iterated over and multiplied together during the expansion, greatly improving average time complexity.
For a vector of dimension $D$ and density $0 \le d \le 1$, the algorithm has time complexity $\Theta(d^KD^K)$ where $K$ is the polynomial-feature order; this  is an improvement by a factor $d^K$ over the standard method.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.
